---
title: "World's End Pub Crawl"
author: "Gabriel Hendergate"
date: "06/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Pub Crawl 2021/07/06

This interactive map plots the route taken by the heroes during "The 
World's End", featuring Simon Pegg and Nick Frost in their final journey - 
known to us survivors as the Cornetto Trilogy. 
Their names have been changed to protect their identities.

Only seven pubs out of the 12 are known to have survived the invasion by 
REDACTED, and these relics have since been taken under new ownership. During the 
short war with REDACTED the town of Newton-Haven was decimated and has 
since been rebuilt as Welwyn Garden City and Letchworth. 
During your pilgrimage to these fine British establishments take a moment to 
remember the loss of your connection to REDACTED, and to forge new friendships 
and old, and to arrange for a horse-drawn cart to take you back home.

Please open each marker to view an illustration of the former pub sign and 
see the name of the new venue.

```{r mapping}
library(leaflet)
# prepare the data
pubs <- data.frame(
    latitude = c(51.790160124758614, 
                 51.80016458093416, 
                 51.802169980552726,
                 51.97928361055955, 
                 51.97941295262207, 
                 51.97784444453014, 
                 51.97953836779092
                 ),
    longitude  = c(-0.19715907765130217,
                   -0.2082224647981939,
                   -0.20746533462751418,
                   -0.22665721990273915,
                   -0.2283959579973739,
                   -0.22968098360747663,
                   -0.25261373479802396
                   )
    )
filmName = c("The First Post",
             "The Old Familiar",
             "The Famous Cock",
             "The Trusty Servant",
             "Two Headed Dog",
             "The King’s Head",
             "The World’s End"
             )
realName = c("1. Pear Tree Inn",
             "2. The Doctors Tonic",
             "3. Two Willows",
             "4. Three Magnets",
             "5. The Platform",
             "6. The Arena Tavern",
             "7. The Wilbury"
             )
pubIcons = icons(iconUrl = c("https://simonpegg.net/wp-content/uploads/2013/07/firstpost-728x1024.jpg",
        "https://simonpegg.net/wp-content/uploads/2013/07/oldfamiliar-719x1024.jpg",
        "https://simonpegg.net/wp-content/uploads/2013/07/famouscock.jpg",
        "https://simonpegg.net/wp-content/uploads/2013/07/trustyservant-667x1024.jpg",
        "https://simonpegg.net/wp-content/uploads/2013/07/twoheadeddog-783x1024.jpg",
        "https://simonpegg.net/wp-content/uploads/2013/07/thekingshead.jpg",
        "https://simonpegg.net/wp-content/uploads/2013/07/theworldsendpub-707x1024.jpg"
        ),
        iconWidth = rep("73.4", 7),
        iconHeight = rep("100", 7)
)
# create html syntax for images
pubUrls = c()
for (i in seq(1:length(pubIcons$iconUrl))) {
    pubUrls[i] <- paste("<img src = ", pubIcons$iconUrl[i], 
                        " width = ", pubIcons$iconWidth[i], 
                        " height = ", pubIcons$iconHeight[i],
                        ">")
}
 
# generate the map
pubs %>%
    leaflet() %>%
    addTiles() %>%
    addMarkers(popup = pubUrls,
               label = realName) %>%
    addPolylines(data = pubs, lng = ~longitude, lat = ~latitude)
```

